Simulation study in rectangular domain

### 2024-05-12 R/simulation_study_CRCVM/simulation_study_fjords.Rmd
reset simulation study

ftau_bump=function(cov_data,epsilon=pi/10,alpha=pi/5,D0=1,tau0=0.8,tau1=2) {
    Dshore=cov_data$DistanceShore
    theta=cov_data$theta
    tau=(tau0+(tau1-tau0)*(tanh((theta+(pi/2+epsilon))/alpha)-tanh((theta+(pi/2-epsilon))/alpha))+
      (tau1-tau0)*(tanh((theta+(-pi/2+epsilon))/alpha)-tanh((theta+(-pi/2-epsilon))/alpha)))
    return (tau)
}

>>>>

ftau_bump=function(cov_data,epsilon=pi/8,alpha=pi/5,tau0=0.2,tau1=2) {
    Dshore=cov_data$DistanceShore
    theta=cov_data$theta
    tau=(tau0+(tau1-tau0)*(tanh((theta+(pi/2+epsilon))/alpha)-tanh((theta+(pi/2-epsilon))/alpha))+
      (tau1-tau0)*(tanh((theta+(-pi/2+epsilon))/alpha)-tanh((theta+(-pi/2-epsilon))/alpha)))
    return (tau)
}

### 2024-05-12 R/simulation_study_CRCVM/simulation_study_rect.Rmd
reset simulation study

#some auxiliary functions
source("CVM_functions.R")
```

@@

#degree of freedom in tensor splines
SP_DF=3

@@

```{r time steps}
#time step
hf=1/60

@@

Dshore=seq(from=0.3,to=2,length.out=30)
theta=seq(from=-pi,to=pi,length.out=30)
grid<- as.data.frame(expand.grid(Dshore,theta))
colnames(grid)=c("DistanceShore","theta")
spline_omega=matrix(fomega_splines(grid),30,30)

@@

### Generate samples

```{r illustrative sample for the paper}

res=sim_theta_CRCVM(ftau=ftau_constant,fomega=fomega,fnu=fnu_constant,v0=v0,x0=x0[1,],times=seq(0,2*24,by=1/60),land=domain,verbose=FALSE)

data_sim=res$sim
data_sim$ID=factor(rep(1,length(data_sim$y1)))
data_shore=res$shore[,c("p1","p2")]
data_sim=cbind(data_sim,data_shore)

data_sim=data_sim[seq(1,length(data_sim$time),by=5),]

plot_illust_rect=ggplot()+geom_sf(data=domain$geometry,fill="grey")+coord_sf(datum=st_crs(32626))+
  geom_point(data=data_sim,aes(p1,p2),shape=5,size=0.1,col="red")+
  geom_point(data=data_sim,mapping=aes(y1,y2),size=0.1)+
  geom_path(data=data_sim,mapping=aes(y1,y2),size=0.1)+
  geom_point(data = data_sim%>% filter(!duplicated(ID)),
             aes(x = y1, y = y2), shape = 3, size = 4, col = "red")+
  xlab("x") + ylab("y")

plot_illust_rect

ggsave(filename="illustrative_sample_rect.png",plot=plot_illust_rect,width=10,height=5)
```

```{r parallel generate batches of hf low errors samples,cache=TRUE}

#setup parallel backend to use many processors
cores=detectCores()
cl <- makeCluster(cores[1]-1) #not to overload your computer
registerDoParallel(cl)

data_rect_hf_ne <- foreach(k=1:N_BATCH,.packages=c("progress","MASS","sf","foreach","mgcv")) %dopar% {
  data=foreach (i=1:N_ID,.combine='rbind') %do% {

@@

    data_sim=res$sim
    data_sim$ID=factor(rep(i,length(data_sim$y1)))
    data_shore=res$shore[,c("p1","p2")]
    cbind(data_sim,data_shore)
  }
  data 
}

#stop cluster
stopCluster(cl)

names(data_rect_hf_ne)=paste("BATCH",1:N_BATCH,sep="")
```

### percentage of samples that reached land

```{r percentage of low error samples that reached land}
count=0
for (k in 1:length(names(data_rect_hf_ne))) {

  data=data_rect_hf_ne[[paste("BATCH",k,sep="")]]
  for (id in unique(data$ID)) {
    sub_data=data[data$ID==id,]
    if (nrow(sub_data) < n_hf) {
      count=count+1
      cat(paste("BATCH",k,sep=""),":",id,"\n",sep=" ")
    }
  }
}
cat(count/(N_BATCH*N_ID)*100,"percent of the samples reached land")
```

@@

plot_samples_rect_hf_ne=ggplot()+geom_sf(data=domain$geometry,fill="grey")+coord_sf(datum=st_crs(32626))+
  geom_point(data=data_rect_hf_ne$BATCH1,aes(p1,p2),shape=5,size=0.1,col="red")+
  geom_point(data=data_rect_hf_ne$BATCH1,mapping=aes(y1,y2,color=ID,shape=ID),size=0.1)+
  geom_path(data=data_rect_hf_ne$BATCH1,mapping=aes(y1,y2,color=ID,shape=ID),size=0.1)+
  geom_point(data = data_rect_hf_ne$BATCH1%>% filter(!duplicated(ID)),
             aes(x = y1, y = y2), shape = 3, size = 4, col = "red")+
  xlab("x") + ylab("y")

>>>>

#some auxiliary functions
par_dir=dirname(getwd())
source(file.path(par_dir,"CVM_functions.R"))
```

@@

#degree of freedom in tensor splines
SP_DF=4

@@

```{r time steps}
#time step
hf=1/120

@@

Dshore=seq(from=0.3,to=4,length.out=30)
theta=seq(from=-pi,to=pi,length.out=30)
grid<- as.data.frame(expand.grid(Dshore,theta))
colnames(grid)=c("DistanceShore","theta")
spline_omega=matrix(fomega_splines(grid),30,30)

@@

```{r generate batch of hf low errors samples,cache=TRUE}

data_rect_hf_ne =foreach (i=1:N_ID,.combine='rbind') %do% {

@@

    data_sim=res$sim
    data_sim$ID=factor(rep(i,length(data_sim$y1)))
    data_shore=res$shore[,c("p1","p2")]
    cbind(data_sim,data_shore)
}

@@

plot_samples_rect_hf_ne=ggplot()+geom_sf(data=domain$geometry,fill="grey")+coord_sf(datum=st_crs(32626))+
  geom_point(data=data_rect_hf_ne,aes(p1,p2),shape=5,size=0.1,col="red")+
  geom_point(data=data_rect_hf_ne,mapping=aes(y1,y2,color=ID,shape=ID),size=0.1)+
  geom_path(data=data_rect_hf_ne,mapping=aes(y1,y2,color=ID,shape=ID),size=0.1)+
  geom_point(data = data_rect_hf_ne%>% filter(!duplicated(ID)),
             aes(x = y1, y = y2), shape = 3, size = 4, col = "red")+
  xlab("x") + ylab("y")
